---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(dplyr)
library(DBI)
library(dbplyr)
library(odbc)

odbcListDrivers()

con <- DBI::dbConnect(odbc(),
                      Driver = "SQL Server",
                      Server = "mcobsql.business.nd.edu",
                      UID = "MSBAstudent",
                      PWD = "SQL%database!Mendoza",
                      Port = 3306, 
                      Database = "ChicagoCrime")

dbListFields(con, "wards")

dbListFields(con, "crimes")

select_q <- dbSendQuery(
  conn = con, 
  statement = "SELECT ward, percentIncomeUnder25K FROM wards"
)

select_res <- dbFetch(select_q)

dbClearResult(select_q)

# Rocking with over 2 million rows in crimes

select_q <- dbSendQuery(
  conn = con, 
  statement = "SELECT id, ward, locationType, arrest 
  FROM crimes WHERE arrest='TRUE' AND locationType='RESIDENCE'"
)

select_res <- dbFetch(select_q)

# Now we are down to under 45K!

dbClearResult(select_q)

longer_statement <- "
SELECT locationType, COUNT(*) AS 'count'
FROM crimes 
GROUP BY locationType
ORDER BY count DESC
"

my_query <- gsub("\\n|\\s+", " ", longer_statement)

select_q <- dbSendQuery(conn = con, 
                        statement = my_query)

select_res <- dbFetch(select_q)

dbClearResult(select_q)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
